\itshape Exploring Multi-scale Spatiotemporal Twitter User Mobility Patterns Using Geo-located Twitter Data

### 2016-05-08 MovePattern_revision/Twitter_MovementPatterns_VisualAnalytics.tex
home

\section{Introduction}
Understanding human mobility patterns is of great importance for a broad range of applications from urban planning~\citep{zheng2008understanding}, traffic management~\citep{jiang2009characterizing}, and even the spatial spread of epidemic diseases~\citep{belik2011natural}.
Earlier research efforts relied on low resolution mobility data to understand human mobility patterns, such as using census records to understand human migration patterns~\citep{greenwood1985human}, or delivering questionnaires and asking volunteers to report the track of bank notes to infer human travel patterns~\citep{brockmann2006scaling}.
However, the lack of detailed human movements with fine-grained spatial and temporal granularity limits the findings to capture mobility patterns of individuals~\citep{gonzalez2008understanding,Jurdak2015}.
In addition to the mobility data collected by GPS trackers~\citep{zheng2008understanding, rhee2011levy} and mobile phone call records~\citep{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}, 
emerging as a new source for mobility data, today's pervasive Location Based Social Media (LBSM) platforms (e.g., Twitter and Foursquare) offer continuous spatial Big Data streams with massive amount of detailed and frequently updated user digital footprints~\citep{thatcher2014living} in the form of real-world trails and footprints.
One significant advantage of LBSM data streams is the large spatial coverage, for example, researchers have used geo-located Twitter data for studying global mobility patterns~\citep{hawelka2014geo}, which is otherwise impossible by using other mobility datasets (e.g., GPS traces and mobile phone call records). 
In addition, the publicly available LBSM data streams offer unique opportunities for conducting reproducible scientific findings regarding the concerns of infringement on individual privacy, such as using mobile phone call records~\citep{giannotti2008mobility,crampton2014collect,Jurdak2015}.

@@

Another approach from the literatures for studying human mobility is using mobile phone call data in the form of Call Detail Records (CDR), where the locations of mobile users are estimated by cell tower triangulation with accuracy in the order of kilometers~\citep{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}. 
Such a dataset can cover relatively large spatial scale (e.g., country level)~\citep{becker2013human,sobolevsky2013delineating} and a large portion of the population in the study region~\citep{kung2014exploring}. However, due to the concerns of infringement on individual privacy, the mobile phone call data is not publicly accessible, which is not ideal  for conducting reproducible scientific findings, such as validating or extending the existing discoveries.

@@

More importantly, as our framework can aggregate Twitter user trajectories within different temporal ranges, we further analyzed the probability distributions of accumulated displacements took places in January, June, and October (Figure 5 (d)) and radius of gyrations within 4 quarters in year 2014 (Figure 7), in order to examine whether there are temporal changes in the mobility patterns. While the probability distributions of accumulated displacements are almost identical in those selected three months,  we do find changes in the probability distributions of radius of gyrations in different quarters of the year. 
The fluctuations in the tails of the distributions indicate that long distance radius of gyrations (i.e., above 30 km) will experience more seasonal changes in the Twitter user mobility pattern, which means the increase or decrease of long distance movement activities in the corresponding time period. 
However, it is worthy noting that the overall trends in the Twitter user mobility patterns revealed by radius of gyrations are still consistent.  In summary, by comparing these results with the same measurements in~\citep{Jurdak2015}, (slightly) different distance bounds were identified for describing the Twitter user mobility patterns in the USA and Australia, however the overall similarity and consistence found in using a combination of three functions to approximate the probability distribution functions of displacements and radius of gyrations, clearly provide supports for using geo-located tweets for conducting reproducible human mobility studies.

@@

We studied the distance decay effects in the collective Twitter user movements measured by the probability distributions of the displacements and radius of gyrations of individuals. 
These distributions can all be approximated by a combination of three functions: an exponential function, a stretched-exponential function and a power-law function. In particular, distance bounds between different fitting functions in displacement distribution reveals the existence of multi-scale or multi-modal mobility patterns of the Twitter users in the United States, whereas the distribution of radius of gyration reveals different groups of Tweet users with different types of spatial coverages.   
More importantly, we further studied these mobility patterns in different temporal scales to investigate the temporal changes in the mobility patterns. 
We found that the accumulated displacements are almost identical in different months, while the long distance radius of gyration (i.e., above 30 km) will experience more seasonal changes in the Twitter user mobility pattern.
In particular, by comparing the mobility patterns revealed by displacements and radius of gyrations of Twitter users in the United States and Australia, there are slightly difference regarding the exact value of distance bounds between different fitting functions. 
However, the fact that these measurements are of people (i.e., Twitter users) in different countries (in this case, continent) and their probability distributions can all be approximated by a combination of three functions, has clearly show the values in using geo-located tweets for conducting reproducible human mobility studies.

>>>>

\section{Introduction}
Understanding human mobility patterns is of great importance for a broad range of applications from urban planning~\citep{zheng2008understanding}, traffic management~\citep{jiang2009characterizing}, and even the spatial spread of epidemic diseases~\citep{belik2011natural}.
Earlier research efforts relied on low resolution mobility data to understand human mobility patterns, such as using census records to understand human migration patterns~\citep{greenwood1985human}, or delivering questionnaires and asking volunteers to report the track of bank notes to infer human travel patterns~\citep{brockmann2006scaling}.
However, the lack of detailed human movements with fine-grained spatial and temporal granularity limits the findings to capture mobility patterns of individuals~\citep{gonzalez2008understanding,Jurdak2015}.
In addition to the mobility data collected by GPS trackers~\citep{zheng2008understanding, rhee2011levy} and mobile phone call records~\citep{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}, 
emerging as a new source for mobility data, today's pervasive Location Based Social Media (LBSM) platforms (e.g., Twitter and Foursquare) offer continuous spatial Big Data streams with massive amount of detailed and frequently updated user digital footprints~\citep{thatcher2014living} in the form of real-world trails and footprints.
One significant advantage of LBSM data streams is the large spatial coverage, for example, researchers have used geo-located Twitter data for studying global mobility patterns~\citep{hawelka2014geo}, which is otherwise impossible by using other mobility datasets (e.g., GPS traces and mobile phone call records). 
In addition, the publicly available LBSM data streams offer unique opportunities for conducting replicable scientific findings regarding the concerns of infringement on individual privacy, such as using mobile phone call records~\citep{giannotti2008mobility,crampton2014collect,Jurdak2015}.

@@

Another approach from the literatures for studying human mobility is using mobile phone call data in the form of Call Detail Records (CDR), where the locations of mobile users are estimated by cell tower triangulation with accuracy in the order of kilometers~\citep{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}. 
Such a dataset can cover relatively large spatial scale (e.g., country level)~\citep{becker2013human,sobolevsky2013delineating} and a large portion of the population in the study region~\citep{kung2014exploring}. However, due to the concerns of infringement on individual privacy, the mobile phone call data is not publicly accessible, which is not ideal  for conducting replicable scientific findings, such as validating or extending the existing discoveries.

@@

More importantly, as our framework can aggregate Twitter user trajectories within different temporal ranges, we further analyzed the probability distributions of accumulated displacements took places in January, June, and October (Figure 5 (d)) and radius of gyrations within 4 quarters in year 2014 (Figure 7), in order to examine whether there are temporal changes in the mobility patterns. While the probability distributions of accumulated displacements are almost identical in those selected three months,  we do find changes in the probability distributions of radius of gyrations in different quarters of the year. 
The fluctuations in the tails of the distributions indicate that long distance radius of gyrations (i.e., above 30 km) will experience more seasonal changes in the Twitter user mobility pattern, which means the increase or decrease of long distance movement activities in the corresponding time period. 
However, it is worthy noting that the overall trends in the Twitter user mobility patterns revealed by radius of gyrations are still consistent.  In summary, by comparing these results with the same measurements in~\citep{Jurdak2015}, (slightly) different distance bounds were identified for describing the Twitter user mobility patterns in the USA and Australia, however the overall similarity and consistence found in using a combination of three functions to approximate the probability distribution functions of displacements and radius of gyrations, clearly provide supports for using geo-located tweets for conducting replicable human mobility studies.

@@

We studied the distance decay effects in the collective Twitter user movements measured by the probability distributions of the displacements and radius of gyrations of individuals. 
These distributions can all be approximated by a combination of three functions: an exponential function, a stretched-exponential function and a power-law function. In particular, distance bounds between different fitting functions in displacement distribution reveals the existence of multi-scale or multi-modal mobility patterns of the Twitter users in the United States, whereas the distribution of radius of gyration reveals different groups of Tweet users with different types of spatial coverages.   
More importantly, we further studied these mobility patterns in different temporal scales to investigate the temporal changes in the mobility patterns. 
We found that the accumulated displacements are almost identical in different months, while the long distance radius of gyration (i.e., above 30 km) will experience more seasonal changes in the Twitter user mobility pattern.
In particular, by comparing the mobility patterns revealed by displacements and radius of gyrations of Twitter users in the United States and Australia, there are slightly difference regarding the exact value of distance bounds between different fitting functions. 
However, the fact that these measurements are of people (i.e., Twitter users) in different countries (in this case, continent) and their probability distributions can all be approximated by a combination of three functions, has clearly show the values in using geo-located tweets for conducting replicable human mobility studies.
